The QCD $ZZjj$ production is an irreducible background in the search for EW $ZZjj$ production.
This process is estimated from simulation via a data-driven correction for its normalization in the \lllljj channel, and estimated purely from simulation in the \llvvjj channel.
For the $ggZZjj$ process, an additional $K$-factor of 1.7~\cite{PhysRevD.92.094028} is applied to account for the NLO QCD correction.
In the \lllljj channel, the normalization of the QCD $ZZjj$ processes is constrained by a dedicated control region (CR) defined in data by reverting either the \mjj or \dyjj requirements,
and is then included as a floating parameter in the statistical fit to properly treat the uncertainty correlations between SR and CR.
This CR cannot be defined in the \llvvjj channel, due to large contributions from reducible background.

In the \lllljj channel, background contributions from \Zjet, top-quark and $WZ$ processes are estimated from data.
These events may contain two or three isolated leptons from $Z$ or $W$ decays, together with heavy-flavour jets or misidentified components of jets yielding reconstructed leptons, i.e. `fake-leptons'.
These `fake-lepton' backgrounds are estimated using a method similar to that described in Ref.~\cite{Aaboud:2017rwm},
where the lepton misidentification is measured in data regions with enhanced contributions from \Zjet and top-quark processes.
Small background contributions from triboson and $ttV$ production are estimated from simulation.
Backgrounds from all these non-$ZZ$ processes collectively yield an estimated contribution of about 3\% to the selected data sample. These minor backgrounds are hereafter referred to as ``Others'' in the \lllljj channel.

In the \llvvjj channel, the QCD $ZZjj$ processes constitute 26\% of the selected sample,
and the remaining major backgrounds originate from $WZjj$ (29\%), $WWjj$ and \ttbar~production (27\%).
The $WZjj$ background is estimated using a data CR defined by requiring three selected leptons and a looser event selection, following the methodology explained in Ref.~\cite{Aaboud:2017bja}.
The simulation is found to overestimate the $WZjj$ contribution by 15\% in this CR in data,
and therefore, the $WZjj$ yield in the SR is scaled by 0.85.
The $WZjj$ estimate is found to have a relative uncertainty of 5\%, due to the data statistical uncertainty in the CR as well as the experimental and theoretical uncertainties.
The $WZjj$ distribution of the MD is evaluated from simulation with the EW $WZjj$ normalisation scaled by 1.77, corresponding to the difference between data and simulation observed in a previous analysis, in a similar phase space~\cite{Aaboud:2018ddq},
where the overall normalization factor is found to be consistent with the one derived in this note.
The $WZjj$ shape uncertainty originates from experimental and theoretical uncertainties as well as from the uncertainty in the quoted EW $WZjj$ cross-section measurement.
The \nonresll~background, including the $WWjj$ and \ttbar~processes, contain genuine \met~and a lepton pair not originating from a $Z$ or a $\gamma^{*}$-boson decay.
This background is estimated using a CR selected in data by requiring the same selection as in the SR with the exception that an $e\mu$ pair is required, following the methodology explained in Ref.~\cite{Aaboud:2017bja}.
The \nonresll~estimate has a relative uncertainty of 20\%, dominated by the data statistical uncertainty in the CR.
The MD distribution for the \nonresll~process is estimated from simulation,
with an uncertainty assigned to account for the difference between shapes in data and simulation.
The \Zjet background is largely suppressed, and the yield is evaluated by extrapolating the low \met-significance region distribution in data to the high \met-significance region using an exponential function,
while the MD distribution in the SR is modeled by simulation.
A conservative uncertainty is assigned to account for variations in the fitting functions as well as differences between estimated and simulated yields and distributions.
In addition, triboson and $ttV$ backgrounds are modelled with simulation. Similar to the \lllljj channel, these minor backgrounds are denoted as ``Others''.

The observed and expected yields are listed in Table~\ref{tab:yield_prefit},
where in total 127 (82) data events are selected in the \lllljj (\llvvjj) channel.
No significant deviation from the SM prediction is observed.

\begin{table}[!htbp]
\sisetup{
table-number-alignment = center,
table-align-uncertainty=true
}
\begin{center}

% \begin{tabular}{c|c|c}
% \hline
% Process                 & \lllljj          & \llvvjj           \\
% \hline
% EW $ZZjj$               &  $20.6 \pm  2.5$ & $12.3 \pm 0.7$  \\
% QCD $ZZjj$              &  $77.4 \pm 25.0$ & $17.2 \pm 3.5$  \\
% QCD $ggZZjj$            &  $13.1 \pm  4.4$ & $ 3.5 \pm 1.1$  \\
% Non-resonant-$\ell\ell$ &  -               & $21.4 \pm 4.8$  \\
% $WZ$                    &  -               & $22.8 \pm 1.1$  \\
% Others                  &  $ 3.2 \pm  2.1$ & $ 1.2 \pm 0.9$  \\
% \hline
% Total                   & $114.3 \pm 25.6$ & $78.4 \pm 6.2$  \\
% \hline
% Data                    &  127             & 82              \\
% \hline
% \end{tabular}


\begin{tabular}{
c
S[table-format = 3.1]@{$\,\pm\,$}
S[table-format = 2.1]
S[table-format = 2.2]@{$\,\pm\,$}
S[table-format = 1.2]
}
%\hline
%Process                 & \multicolumn{2}{c}{\lllljj}    & \multicolumn{2}{c}{\llvvjj}           \\
%\hline
%EW $ZZjj$               &  20.6 &  2.5 & 12.3 & 0.7  \\
%QCD $ZZjj$              &  77.4 & 25.0 & 17.2 & 3.5  \\
%QCD $ggZZjj$            &  13.1 &  4.4 & 3.5 & 1.1  \\
%Non-resonant-$\ell\ell$ &  \multicolumn{2}{c}{-} & 21.4 & 4.8  \\
%$WZ$                    &  \multicolumn{2}{c}{-} & 22.8 & 1.1  \\
%Others                  &   3.2 &  2.1 & 1.2 & 0.9  \\
%\hline
%Total                   & 114.3 & 25.6 & 78.4 & 6.2  \\
%\hline
%Data                    &  \multicolumn{2}{l}{127}    & \multicolumn{2}{l}{82}  \\
%\hline
%\end{tabular}
\hline
Process                 & \multicolumn{2}{c}{\lllljj}    & \multicolumn{2}{c}{\llvvjj}           \\
\hline
EW $ZZjj$               &  20.6 &  2.5 & 12.30 & 0.65  \\
QCD $ZZjj$              &  77   & 25   & 17.2  & 3.5  \\
QCD $ggZZjj$            &  13.1 &  4.4 &  3.5  & 1.1  \\
Non-resonant-$\ell\ell$ &  \multicolumn{2}{c}{-} & 21.4 & 4.8  \\
$WZ$                    &  \multicolumn{2}{c}{-} & 22.8 & 1.1  \\
Others                  &   3.2 &  2.1 & 1.15  & 0.89  \\
\hline
Total                   & 114   & 26   & 78.4 & 6.2  \\
\hline
Data                    &  \multicolumn{2}{l}{127}    & \multicolumn{2}{l}{82}  \\
\hline
\end{tabular}


\end{center}
\caption{
Observed data and expected signal and background yields in 139~\ifb{} of data.
Minor backgrounds are summed together as `Others'.
Uncertainties on the predictions include both statistical and systematic components.
}
\label{tab:yield_prefit}
\end{table}


